---
title: "the project 1 part 1"
author: "wangh"
date: "Saturday, August 16, 2014"
output: html_document
---

Illustrate via simulation and associated explanatory text the properties of the distribution of the mean of 40 exponential(0.2)s. 
```{r}
set.seed(2)
library(data.table)
library(ggplot2)
```
#### Q1.Show where the distribution is centered at and compare it to the theoretical center of the distribution.
```{r}
nosim <- 1000
n<-40
lambda<-0.2
mean(apply(matrix(rexp(nosim*n, lambda), ncol=n), 1, mean))
1/lambda
```
They are nearly.

#### Q2. Show how variable it is and compare it to the theoretical variance of the distribution.
```{r}
nosim <- 1000
n<-40
lambda<-0.2
sd(apply(matrix(rexp(nosim*n, lambda), ncol=n), 1, mean))^2
(1/lambda)^2/n
```
They are nearly.

#### Q3. Show that the distribution is approximately normal.
```{r}
nosim <- 1000
n<-40
lambda<-0.2
df<-data.table(average=apply(matrix(rexp(nosim*n, lambda), ncol=n), 1, mean))
```
```{r,echo=FALSE,fig.height=3}
g <- ggplot(df, aes(x = average)) + labs(title = paste('miu = ', 1/lambda))
g <- g + geom_histogram(fill = "salmon",binwidth=0.1, aes(y = ..density..), colour = "black")
g <- g + geom_density(size = 1) + geom_vline(xintercept = 1/lambda, size =1)
g
```

#### Q4:Evaluate the coverage of the confidence interval for 1/lambda
```{r}
lambdavals <- seq(0.05, 2.0, by = 0.05)
nosim <- 1000
myLambcov<-function(lambda) {
  xhats<-matrix(rexp(nosim*n, lambda), ncol=n)
  miu<-apply(xhats, 1, mean)
  S<-apply(xhats, 1, sd)
  ll <- miu - 1.96*S/sqrt(n)
  ul <- miu + 1.96*S/sqrt(n)
  mean(ll < 1/lambda & ul > 1/lambda)
}  
n<-40; coverage40 <- sapply(lambdavals, myLambcov )
n<-400; coverage400 <- sapply(lambdavals, myLambcov)
```
```{r,echo=FALSE,fig.height=3}
dat<-rbind(data.frame(sno=40,lambdavals,coverage=coverage40),data.frame(sno=400,lambdavals,coverage=coverage400))

g <- ggplot() 
g <- g + geom_line(data=data.frame(lambdavals,coverage40), aes(x=lambdavals,y=coverage40,color="40"),size=1)
g <- g + geom_line(data=data.frame(lambdavals,coverage400), aes(x=lambdavals,y=coverage400,color="400"),size=1)
g <- g + scale_colour_manual("# of samples",values = c("40" = "red","400" = "blue"))
g <- g + geom_hline(yintercept = 0.95)
g <- g + coord_cartesian(ylim = c(0.85,1))
g
```
