---
output: html_document
---
the project for the statistical inference class
========================================================

This is the project for the statistical inference class. In it, you will use simulation to explore inference and do some simple inferential data analysis. 

# Part 1
Illustrate via simulation and associated explanatory text the properties of the distribution of the mean of 40 exponential(0.2)s. 

### Q1.Show where the distribution is centered at and compare it to the theoretical center of the distribution.

where the distribution is center:
```{r}
nosim <- 1000
n<-40
lambda<-0.2
mean(apply(matrix(rexp(nosim*n, lambda), ncol=n), 1, mean))
```
theoretical center of the distribution
```{r}
1/lambda
```

They are almost same.

### Q2. Show how variable it is and compare it to the theoretical variance of the distribution.

```{r}
nosim <- 1000
n<-40
lambda<-0.2
sd(apply(matrix(rexp(nosim*n, lambda), ncol=n), 1, mean))^2
```
the theoretical variance of the distribution
```{r}
(1/lambda)^2/n
```
They are almost same.

### Q3. Show that the distribution is approximately normal.
```{r,fig.height=3}
library(data.table)
nosim <- 1000
n<-40
lambda<-0.2
df<-data.table(average=apply(matrix(rexp(nosim*n, lambda), ncol=n), 1, mean))

library(ggplot2)

g <- ggplot(df, aes(x = average))
g <- g + geom_histogram(fill = "salmon",binwidth=0.1, aes(y = ..density..), colour = "black")
g <- g + geom_density(size = 2)
g <- g + geom_vline(xintercept = 1/lambda, size = 2)
miu<-1/lambda
g <- g + labs(title = paste('miu = ', miu))
g
```

### Q4:Evaluate the coverage of the confidence interval for 1/lambda

```{r,fig.height=3}
lambdavals <- seq(0.05, 2.0, by = 0.05)
nosim <- 1000
n<-400
coverage <- sapply(lambdavals, function(lambda) {
  xhats<-matrix(rexp(nosim*n, lambda), ncol=n)
  miu<-apply(xhats, 1, mean)
  S<-apply(xhats, 1, sd)
  ll <- miu - 1.96*S/sqrt(n)
  ul <- miu + 1.96*S/sqrt(n)
  mean(ll < 1/lambda & ul > 1/lambda)
})

library(ggplot2)
g <- ggplot(data.frame(lambdavals,coverage), aes(x = lambdavals, y=coverage))
g <- g + geom_line(size=2)
g <- g + geom_hline(yintercept = 0.95)
g <- g + coord_cartesian(ylim = c(0.85,1))
g
```
