the project for the statistical inference class
========================================================

This is the project for the statistical inference class. In it, you will use simulation to explore inference and do some simple inferential data analysis. The project consists of two parts:

The exponential distribution can be simulated in R with rexp(nosim, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also also 1/lambda. Set lambda = 0.2 for all of the simulations. In this simulation, you will investigate the distribution of averages of 40 exponential(0.2)s. Note that you will need to do a thousand or so simulated averages of 40 exponentials.

```{r}
nosim <- 1000
n<-40
lambda<-0.2
p<-apply(matrix(rexp(nosim*n, lambda), nosim), 1, mean)
```

1.Show where the distribution is centered at and compare it to the theoretical center of the distribution.
```{r}
mean(p)
```
theoretical center of the distribution
```{r}
1/lambda
```

2. Show how variable it is and compare it to the theoretical variance of the distribution.
```{r}
sd(p)
```
theoretical center of the distribution
```{r}
1/lambda/sqrt(n)
```

3. Show that the distribution is approximately normal.
```{r}
g <- ggplot(p)
  g <- g + geom_histogram(fill = "salmon",binwidth=1, aes(y = ..density..), colour = "black")
  g <- g + geom_density(size = 2)
  g <- g + geom_vline(xintercept = p, size = 2)
  mse <- round(mean((galton$child - mu)^2), 3)
  g <- g + labs(title = paste('mu = ', mu, ' MSE = ', mse))
  g

```
