---
title: "the project 1 part 2"
author: "wangh"
date: "Saturday, August 16, 2014"
output: html_document
---

analyze the ToothGrowth data in the R datasets package

#### Load the ToothGrowth data
```{r,fig.height=4}
library(datasets)
data(ToothGrowth)
par(mfrow = c(1, 2))
boxplot(len~supp, data=ToothGrowth, main="boxplot(len~supp)")
boxplot(len~dose, data=ToothGrowth,main="boxplot(len~dose)")
coplot(len ~ dose | supp, data = ToothGrowth, panel = panel.smooth,
       xlab = "ToothGrowth data: length vs dose, given type of supplement")
```

#### compare tooth growth by supp
```{r}
g_VC<-ToothGrowth[ToothGrowth$supp=="VC","len"]
g_OJ<-ToothGrowth[ToothGrowth$supp=="OJ","len"]
diff=g_OJ - g_VC
mean(diff)
```
test the hypothesis: H0:diff=3 versus Ha:diff<>3
```{r}
tt<-t.test(diff,mu=3); tt
qt(0.975,29)
```
the TS(t=`r tt$statistic`) < qt(0.975,`r tt$parameter`)(=`r qt(0.975,tt$parameter)`), p-value(=`r tt$p.value`)>0.05, so we fail to reject the null hypothesis.

###### So, by 95%, tooth growth by OJ is larger than VC about 3 unit.

#### compare tooth growth by dose
```{r}
diff2=ToothGrowth$len/ToothGrowth$dose
mean(diff2)
```
test the hypothesis: H0:diff=17 versus Ha:diff<>17
```{r}
tt2<-t.test(diff2,mu=17); tt2
qt(0.975,59)
```
the TS(t=`r tt2$statistic`) < qt(0.975,`r tt2$parameter`)(=`r qt(0.975,tt2$parameter)`), p-value(=`r tt2$p.value`)>0.05, so we fail to reject the null hypothesis. 

###### So, by 95%, tooth growth for one unit dose is a constance 17.
