---
title: "the project 1 part 2"
author: "wangh"
date: "Saturday, August 16, 2014"
output: html_document
---
analyze the ToothGrowth data in the R datasets package

### Load the ToothGrowth data
```{r,fig.height=3}
library(datasets)
data(ToothGrowth)
ToothGrowth$dose=as.factor(ToothGrowth$dose)
ag<-rbind(aggregate(len~.,data=ToothGrowth, mean),data.frame(supp="VC+OJ", aggregate(len~dose,data=ToothGrowth, mean)))
xtabs(len~., data=ag)
```
```{r,echo=FALSE}
boxplot(len ~ dose, data = ToothGrowth,
        boxwex = 0.25, at = 1:3 - 0.2,
        subset = supp == "VC", col = "yellow",
        main = "Tooth Growth",
        xlab = "dose(mg)",
        ylab = "tooth length",
        xlim = c(0.5, 3.5), ylim = c(0, 35), yaxs = "i")
boxplot(len ~ dose, data = ToothGrowth, add = TRUE,
        boxwex = 0.25, at = 1:3 + 0.2,
        subset = supp == "OJ", col = "orange")
legend("bottomright", c("VC", "OJ"), fill = c("yellow", "orange"))
```

### Tooth Growth vs supp when dose in (0.5,1)
```{r}
g_OJ<- ToothGrowth[ToothGrowth$supp=="OJ" & ToothGrowth$dose %in% c(0.5,1),"len"] 
g_VC<- ToothGrowth[ToothGrowth$supp=="VC" & ToothGrowth$dose %in% c(0.5,1),"len"]
```
confidence interval and test the hypothesis: 
```{r}
alpha<-0.05; 
tt<-t.test(g_OJ,g_VC); tt
```
t>0, T-confidence interval is above 0, so test the hypothes: H0:miu_OJ = miu_VC VS. Ha: miu_OJ > miu_VC
```{r}
qt(1-alpha, 36.55)
qt(1-alpha/2, 36.55)
```
H0 is rejected, because TS(t = `r tt$statistic`) > qt(1-alpha,`r tt$parameter`)( = `r qt(1-alpha,tt$parameter)`), 

So: by 95% confidence interval, tooth growth by OJ is larger than by VC when dose is 0.5 or 1.

### Tooth Growth vs supp when dose=2
```{r}
g_OJ<- ToothGrowth[ToothGrowth$supp=="OJ" & ToothGrowth$dose==2,"len"] 
g_VC<- ToothGrowth[ToothGrowth$supp=="VC" & ToothGrowth$dose==2,"len"]
tt<-t.test(g_OJ,g_VC); tt
```
t<0, T-confidence interval cover 0, so test the hypothes: H0:miu_OJ = miu_VC VS. Ha1: miu_OJ <> miu_VC 
```{r}
qt(1-alpha,14.04)
qt(1-alpha/2,14.04)
```
we fail to reject H0 because:

1. TS(t = `r tt$statistic`) <= qt(alpha,`r tt$parameter`)( = `r qt(alpha,tt$parameter)`): `r tt$statistic <=qt(alpha,tt$parameter)`
2. |TS(t = `r tt$statistic`)| >= qt(1-alpha/2,`r tt$parameter`)( = `r qt(1-alpha/2,tt$parameter)`): `r abs(tt$statistic)>= qt(1-alpha/2,tt$parameter)`
3. TS(t = `r tt$statistic`) >= qt(1-alpha,`r tt$parameter`)( = `r qt(1-alpha,tt$parameter)`): `r tt$statistic >= qt(1-alpha,tt$parameter)`

So,  when dose is 2, tooth growth by OJ and by VC is same.

### Conclusion
When the dose is large enough(2mg), the OJ and the VC are same with each other for tooth growth, while the OJ is better for tooth growth than VC when the dose is not large enough. 
