---
title: "the project 1 part 2"
author: "wangh"
date: "Saturday, August 16, 2014"
output: html_document
---
analyze the ToothGrowth data in the R datasets package

### Load the ToothGrowth data
```{r}
library(datasets); library(ggplot2); data(ToothGrowth)
ToothGrowth$dose=as.factor(ToothGrowth$dose)
summary(ToothGrowth)
ag<-aggregate(len~.,data=ToothGrowth, mean); xtabs(len~., data=ag)
with(ToothGrowth,tapply(len,list(supp,dose), var))
```
```{r,echo=FALSE,fig.height=3.5}
boxplot(len ~ dose, data = ToothGrowth,boxwex = 0.25, at = 1:3 - 0.2,main = "Tooth Growth",
        subset = supp == "VC", col = "yellow",xlab = "dose(mg)",ylab = "tooth length",
        xlim = c(0.5, 3.5), ylim = c(0, 35), yaxs = "i")
boxplot(len ~ dose, data = ToothGrowth, add = TRUE,boxwex = 0.25, at = 1:3 + 0.2,
        subset = supp == "OJ", col = "green")
legend("bottomright", c("VC", "OJ"), fill = c("yellow", "green"))
```
```{r,echo=FALSE,fig.height=3}
qplot(len, data=ToothGrowth,facets=.~supp, color=dose,geom="density")
qplot(len, data=ToothGrowth,facets=.~dose, color=supp,geom="density")
```

From upper exploratory data analyses, We hypothesis that: 

- The len fits approximately normal distribution and for n is only 60, fit T distribution

### Tooth Growth vs supp when dose in (0.5,1)
```{r}
g_OJ<- ToothGrowth[ToothGrowth$supp=="OJ" & ToothGrowth$dose %in% c(0.5,1),"len"] 
g_VC<- ToothGrowth[ToothGrowth$supp=="VC" & ToothGrowth$dose %in% c(0.5,1),"len"]
```
confidence interval and test the hypothesis: 
```{r}
alpha<-0.05; 
tt<-t.test(g_OJ,g_VC); tt
```
t>0, T-confidence interval lower endpoint is above 0, so test the hypothes: H0:miu_OJ = miu_VC VS. Ha: miu_OJ > miu_VC
```{r}
qt(1-alpha, 36.55)
```
H0 is rejected, because TS(t = `r tt$statistic`) > qt(1-alpha,`r tt$parameter`)( = `r qt(1-alpha,tt$parameter)`), 

So: by 95% confidence interval, tooth growth by OJ is larger than by VC when dose is 0.5 or 1.

### Tooth Growth vs supp when dose=2
```{r}
g_OJ<- ToothGrowth[ToothGrowth$supp=="OJ" & ToothGrowth$dose==2,"len"] 
g_VC<- ToothGrowth[ToothGrowth$supp=="VC" & ToothGrowth$dose==2,"len"]
tt<-t.test(g_OJ,g_VC); tt
```
t<0, T-confidence interval cover 0, so test the hypothes: H0:miu_OJ = miu_VC VS. Ha1: miu_OJ <> miu_VC 
```{r}
qt(1-alpha,14.04)
qt(1-alpha/2,14.04)
```
we fail to reject H0 because:

1. TS(t = `r tt$statistic`) <= qt(alpha,`r tt$parameter`)( = `r qt(alpha,tt$parameter)`): `r tt$statistic <=qt(alpha,tt$parameter)`
2. |TS(t = `r tt$statistic`)| >= qt(1-alpha/2,`r tt$parameter`)( = `r qt(1-alpha/2,tt$parameter)`): `r abs(tt$statistic)>= qt(1-alpha/2,tt$parameter)`
3. TS(t = `r tt$statistic`) >= qt(1-alpha,`r tt$parameter`)( = `r qt(1-alpha,tt$parameter)`): `r tt$statistic >= qt(1-alpha,tt$parameter)`

So,  when dose is 2, tooth growth by OJ and by VC is same.

### Conclusion and assumption
Assumption: The Tooth growth fits approximately normal distribution.

Conclusion:

- when the dose is not large enough(<2mg), the OJ is better for tooth growth than VC .
- When the dose is large enough(2mg), the OJ and the VC are same with each other for tooth growth. 
